Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/results.tex
Actually, we have 318 usable samples...

To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection.
Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
We also determined the effectiveness of our approach using bootstrapping cross validation:
We randomly selected 90\% of 320 comments for training set and used the remaining 10\% for the validation set.
The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}.
This validation was repeated for 300 times to estimate the mean and variance of the performance.

@@

From 320 samples, the number of labeled comments were 87, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from every unique similarity and dissimilarity values in our data set.
% \TODO{.......}. 
% \pick{We cannot brute force for every floating number. How did we calculate this?} 
% \dan{I assume Thai used a numerical optimization or root finding routine such as bisection. You iterate until a value is within a given tolerance.}
% Thai sez: answered.

Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score. \pick{I used dummy results. Please change it} \pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}

@@

\begin{table}[h]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data }
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Ground Truth Data} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useless & 69 & 23 & 7 & 6 \\
Useful & 4 & 13 & 24 & 95 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 20 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

>>>>

To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness as described in previous subsection.
Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
We also determined the effectiveness of our approach using bootstrapping cross validation:
We randomly selected 90\% of 320 comments for training set and used the remaining 10\% for the validation set.
The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}.
This validation was repeated for 300 times to estimate the mean and variance of the performance.

@@

From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
To estimate similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from every unique similarity and dissimilarity values in our data set.
% \TODO{.......}. 
% \pick{We cannot brute force for every floating number. How did we calculate this?} 
% \dan{I assume Thai used a numerical optimization or root finding routine such as bisection. You iterate until a value is within a given tolerance.}
% Thai sez: answered.

Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score.
% \pick{I used dummy results. Please change it}
\pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}

@@

\begin{table}[h]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data }
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Ground Truth Data} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useless & 69 & 23 & 7 & 6 \\
Useful & 3 & 12 & 24 & 95 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 20 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}
